What can Issues on GitHub and Google Code tell us about Exception Fragilities in Android?

### 2015-02-11 android-stacks.tex
new title

@@

\title{Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects}

@@

\author{\IEEEauthorblockN{Roberta Coelho\IEEEauthorrefmark{1},
Lucas Almeida\IEEEauthorrefmark{1},
Georgios Gousios\IEEEauthorrefmark{2},
Arie van Deursen\IEEEauthorrefmark{3}
}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Federal University of Rio Grande do Norte\\
Natal, Brazil\\
Email: \texttt{roberta@dimap.ufrn.br,lucas.almeida@ppgsc.ufrn.br}}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Radboud University Nijmegen\\
Nijmegen, The Netherlands\\
Email: \texttt{georgios@cs.ru.nl}}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Delft University of Technology\\
Delft, The Netherlands\\
Email: \texttt{arie.vandeursen@tudelft.nl}}
}

>>>>

\title{What can Issues on GitHub and Google Code tell us about Exception Fragilities in Android? }

@@

%\title{Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects}

@@

\author{\IEEEauthorblockN{Roberta Coelho\IEEEauthorrefmark{1},
Lucas Almeida\IEEEauthorrefmark{1},
Georgios Gousios\IEEEauthorrefmark{2}, 
Arie van Deursen\IEEEauthorrefmark{2}
}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Federal University of Rio Grande do Norte\\
Natal, Brazil\\
Email: \texttt{roberta@dimap.ufrn.br,lucas.almeida@ppgsc.ufrn.br}}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Delft University of Technology\\
Delft, The Netherlands\\
Email: \texttt{\{g.gousios,arie.vandeursen\}@tudelft.nl}}
}
